### 2019-07-25 chapters/4-approach.tex
Add evaluation diagram and modifies text

\input{figures/approach/typescriptDeclarationFilesGenerationMethodBlockDiagram}

@@

@@

\subsection{Overview}
As explained before, the DefinitelyTyped Repository is the official repository for finding declaration files for npm packages. Therefore, the \textit{TypeScript Declaration Files Generation Method} is intended to be used on existing, published npm packages. The generated output TypeScript declaration file is a valid file which can be used for development and uploaded to the DefinitelyTyped Repository.

The method uses an instrumentation framework to gather data flow information and type information at runtime. A second independent block uses the gathered information to generate a TypeScript Declaration File. The signatures obtained from the generated declaration file are used to generate pre and post conditions on a Symbolic Execution Engine in order to build different test cases that explore new execution paths. The code from the test cases is then added to the existing code base. The declaration file is generated again using an expanded code base.

@@

\subsection{Implementation}
\todo{Decir que es un framework. Decir que es tipo una pipeline donde todo se conecta con lo otro. Explicar que por mas que reciba un string como input}

@@

\section{Evaluation}
\subsection{Parsing}
\subsubsection{TypeScript Compiler API}
\subsection{Comparison}
\todo{Number of functions}
\todo{Number of parameters}
\todo{Interfaces}
\todo{methodCall}
\todo{usedAsArgument}
\todo{Syntax \& Semantic Errors}

>>>>

\input{figures/approach/typescript-declaration-files-generation-method/typescriptDeclarationFilesGenerationMethodBlockDiagram.tex}

@@

The feedback loop is not included in the implementation. Exploring new execution paths by creating new test cases will refine the declaration files, i.e. new types will be assigned to different variables, new interfaces will be detected, existing interfaces will be defined more accurately by detecting new properties, etc. From an incremental point of view, actually generating the declaration files from run-time information has to be developed first. A declaration file must exist first so that it can be refined refined afterwards.

@@

\subsection{Implementation}
As explained before, the DefinitelyTyped Repository is the official repository for finding declaration files for npm packages. Therefore, the \textit{TypeScript Declaration Files Generation Method} is intended to be used on existing, published npm packages. The generated output TypeScript declaration file is a valid file which can be used for development and uploaded to the DefinitelyTyped Repository.

The method uses Jalangi as instrumentation framework to gather data flow information and type information at runtime. A second independent block uses the gathered information to generate a TypeScript Declaration File. The signatures obtained from the generated declaration file are used to generate pre and post conditions on a Symbolic Execution Engine in order to build different test cases that explore new execution paths. The code from the test cases is then added to the existing code base. The declaration file is generated again using an expanded code base.

@@

\todo{Decir que es un framework. Decir que es tipo una pipeline donde todo se conecta con lo otro. Explicar que por mas que reciba un string como input}

@@

\section{Evaluation}
\input{figures/approach/evaluation/evaluationDiagram.tex}
\subsection{Parsing}
\subsubsection{TypeScript Compiler API}
\subsection{Comparison}
\todo{Number of functions}
\todo{Number of parameters}
\todo{Interfaces}
\todo{methodCall}
\todo{usedAsArgument}
\todo{Syntax \& Semantic Errors}
